Data Formatting

### 2021-02-19 scripts/data_format.Rmd
deleted some white space

viral loads
```{r}
vl <- data %>% dplyr::select(vl.4:vl.42) %>% distinct() %>% pivot_longer(vl.4:vl.42)
vl$species_code <- as.double(gsub("vl.","",vl$name))
vl %<>% full_join(., names, by="species_code")
vl %<>% mutate(., ln_value = log(value)) %>% mutate(., log10_value = log10(value))
```
`r nrow(vl)` total species; `sum(vl$value>0)`species with non-zero viral loads

@@

#need to remove duplicated rows and determine what to do with NA's
#env_mat <- env %>% column_to_rownames(., var = "siteID")
```
environmental variables are `r colnames(env_mat)`

>>>>

viral loads
```{r}
vl <- data %>% dplyr::select(vl.4:vl.42) %>% distinct() %>% pivot_longer(vl.4:vl.42)
vl$species_code <- as.double(gsub("vl.","",vl$name))
vl %<>% full_join(., names, by="species_code")
vl %<>% mutate(., ln_value = log(value)) %>% mutate(., log10_value = log10(value))
```

`r nrow(vl)` total species; `sum(vl$value>0)`species with non-zero viral loads

@@

#need to remove duplicated rows and determine what to do with NA's
#env_mat <- env %>% column_to_rownames(., var = "siteID")
```

environmental variables are `r colnames(env_mat)`
